A comprehensive Schizosaccharomyces pombe atlas of physical transcription factor interactions with proteins and DNA

### 2024-08-21 index.qmd
add link to bioRxiv

The accompanying manuscript is available at:

- bioRxiv
- ...

>>>>

The accompanying manuscript is available from:

- [bioRxiv](https://www.biorxiv.org/content/10.1101/2024.08.20.607873): 
  **A comprehensive Schizosaccharomyces pombe atlas of physical transcription
  factor interactions with proteins and chromatin.** Skribbe et al.
  bioRxiv 2024.08.20.607873; doi: https://doi.org/10.1101/2024.08.20.607873
